---
title: "Let's Make a Pitch"
date: "6/1/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Why pitch?

- We pitch because the business world requires we do so
- In this case, the pitch will be 5 slides to keep it pithy
- People have short attention spans

## Why this app

- I live in California, a large state with a diverse population
- There's lots of crime in parts, and I want to understand where we fit within the nation

## My state
-Here are some of California's stats on rape, murder, and assault:

```{r}
data(USArrests)
USArrests["California",]
```
California has 9 murders, 276 assaults, and 40.6 rapes per 100,000 people. There are 39.5 million people living in California. Let's calculate the number of each crime per year:

```{r}
39.5*10^6/10^6*USArrests["California",]
```
That's 355 murders, almost 11,000 assaults, and 1604 rapes per year! That's unfortunate. Fun fact, California is also the most urban state, with 91% of the population living in cities. Hmm...

## What the app does
This app allows you to track the crime statistics by state, filtering by urban population. The app will also fit a regression line to your plot, so you can select only the most urban states and fit a line. So cool! Please fund me now!!!
